---
title: "Cake data"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(here)
library(readxl)
library(tidyverse)
```

```{r, include=FALSE}
here::here()

cake_data_final <- read_csv(here("clean_data/final_cakes.csv"))


```

# Dataset Introduction

This dataset gives the ingredients for a number of desserts.
The small data set meant that few assumptions needed to be made.

The steps to clean the data, with appropriate comments, are provided in a
separate script. 
&nbsp;
&nbsp;
&nbsp;
# Analysis


### 1.Which cake has the most cocoa in it?
```{r}
cake_data_final %>% 
  filter(ingredient == "Cocoa") %>%
  slice_max(amount, n = 1)
```

### Answer: One Bowl Chocolate
&nbsp;
&nbsp;
&nbsp;

### 2. For sponge cake, how many cups of ingredients are used in total?
```{r}
cake_data_final%>%
  filter(measure == "cup" & cake == "Sponge") %>% 
  summarise(total = sum(amount))
```

### Answer: 3.5 cups of ingredients are used in total
&nbsp;
&nbsp;
&nbsp;

### 3. How many ingredients are measured in teaspoons?
```{r}
cake_data_final %>% 
  filter(measure == "teaspoon") %>% 
  #need to count each ingredient once only
  distinct(ingredient) %>% 
  summarise(count = n()) 
```

### Answer: 8 ingredients are measured with teaspoons
&nbsp;
&nbsp;
&nbsp;

### 4. Which cake has the most unique ingredients?
```{r}
ingredient_count <- cake_data_final %>% 
  group_by(cake) %>% 
    mutate(total = sum(ingredient_count = n())) 
ingredient_count %>% 
  summarise(cake_total = sum(total)) %>% 
  arrange(cake_total) %>% 
  head(1)
```
### Answer: Buche de Noel has the most unique ingredients
&nbsp;
&nbsp;
&nbsp;

### 5. Which ingredients are used only once?
```{r}
cake_data_final %>%
  group_by(ingredient) %>% 
  summarise(count = n()) %>%
  filter(count == 1)
```
### Answer: 8 ingredients are used only once as listed above
 

